Safe and Robust Formal Synthesis of Digital Controllers\\ for Continuous Plants

### 2018-04-30 automatica/paper.tex
fixed typos in the description of the benchmarks
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

Our benchmark suite consists of 27 SISO models extracted from the 
control literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS, gajic2008optimal};
these models are discretized with different sample times, leading to $191$ different benchmarks
to evaluate our proposal approach.

The \textit{acrobot} plant corresponds to the model of a two-link 
underactuated robot manipulator, named acrobot, linearized by partial 
feedback linearization~\cite{acrobot}.The \textit{antenna} benchmark 
describes the dynamics of the dynamics of the azimuth angle of an antenna 
motion system composed a gearbox, DC motor and amplifiers~\cite{gajic2008optimal}. 
The \textit{ballmaglev} plant corresponds to the discrete model of a simple 
eletromagnet-ball system, where a steel ball is levitated in air by the action 
of an electromagnetic force generated by an electromagnet~\cite{Franklin15}. 
The \textit{bioreactor} benchmark is a linear model identified by least squares 
for the cell mass concentration controlled through dilution rate of a 
bioreactor~\cite{bioreactor}.

@@

There are two continuous stirred tank reactor models named \textit{cstr} and 
\textit{cstrtmp} that describe the PH dynamics of a neutralization reaction 
of an aqueous solution of sodium acetate with hydrochloric acid~\cite{cstr} and 
the temperature of a exothermic reaction~\cite{astrom2006advanced} in a continuous 
flow stirred-tank reactor. The \textit{DC motor} plant describes the velocity 
dynamics of a basic brushed direct current electrical machine.

@@

The \textit{Invpendulum\_cartpos} and \textit{Invpendulum\_pendang} benchmarks
are models for the cart position and the pendulum angle of an inverted pendulum 
plant composed by a point mass must be equilibrated above the pivot point, which is 
mounted on an one degree of freedom cart that moves over a track through a DC motor.

@@

The \textit{Regulator} plant consists of a linear model of a synchronous electrical
machine connected to an  infinite bus~\cite{KOKOTOVIC198023}. The 
\textit{springer-mass damper system} plant is classic model for several mechanical 
systems dynamics. This benchmark describes a mass, which is fixed to a node by means 
of a springer and moves under the action of a input force, damping, and elastic force.
The \textit{steam drum} benchmark describes the linear model for the level dynamics 
of a  boiler steam drum~\cite{boiler}.

The \textit{suspension} benchmark corresponds to the model of a single wheel suspension 
system of a car, {\it i.e.}, the relative motion dynamics of a mass springer damp model, 
which connects the car to one of its wheels.  The \textit{tapedriver} benchmark
corresponds to the model of computer tape driver, \textit{i.e.}, a computer storage device 
used to read and write data on magnetic tapes.

>>>>

Our benchmark suite consists of 27 SISO models extracted from the 
control literature~\cite{acrobot,cstr,CHEN1979389,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS, gajic2008optimal};
these models are discretized with different sample times, leading to $191$ different benchmarks
to evaluate the Na\"ive (Multi-staged) and Abstraction-based CEGIS approaches.

The \textit{acrobot} plant corresponds to the model of a two-link 
underactuated robot manipulator, named acrobot, linearized by partial 
feedback linearization~\cite{acrobot}.The \textit{antenna} benchmark 
describes the dynamics of the azimuth angle of an antenna 
motion system composed by a gearbox, DC motor and amplifiers~\cite{gajic2008optimal}. 
The \textit{ballmaglev} plant corresponds to the discrete model of a simple 
eletromagnet-ball system, where a steel ball is levitated in air by the action 
of an electromagnetic force generated by an electromagnet~\cite{Franklin15}. 
The \textit{bioreactor} benchmark is a linear model identified by least squares 
for the cell mass concentration controlled through dilution rate of a 
bioreactor~\cite{bioreactor}.

@@

There are two continuous stirred tank reactor models named \textit{cstr} and 
\textit{cstrtmp}, which describe the PH dynamics of a neutralization reaction 
of an aqueous solution of sodium acetate with hydrochloric acid~\cite{cstr} and 
the temperature of a exothermic reaction~\cite{astrom2006advanced} in a continuous 
flow stirred-tank reactor. The \textit{DC motor} plant describes the velocity 
dynamics of a basic brushed direct current electrical machine.

@@

The \textit{Invpendulum\_cartpos} and \textit{Invpendulum\_pendang} benchmarks
are models for the cart position and the pendulum angle of an inverted pendulum 
plant composed by a point mass, which must be equilibrated above the pivot point and is 
mounted on an one degree of freedom cart that moves over a track through a DC motor.

@@

The \textit{Regulator} plant consists of a linear model of a synchronous electrical
machine connected to an infinite bus~\cite{KOKOTOVIC198023}. The 
\textit{springer-mass damper system} plant is a classic model for several mechanical 
systems dynamics. This benchmark describes a mass, which is fixed to a node by means 
of a springer and moves under the action of an input force, damping, and elastic force.
The \textit{steam drum} benchmark describes the linear model for the level dynamics 
of a  boiler steam drum~\cite{boiler}.

The \textit{suspension} benchmark corresponds to the model of a single wheel suspension 
system of a car, {\it i.e.}, the relative motion dynamics of a mass springer damp model, 
which connects the car to one of its wheels.  The \textit{tapedriver} benchmark
corresponds to the model of a computer tape driver, \textit{i.e.}, a computer storage device 
used to read and write data on magnetic tapes.
